An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-27 paper/6.related-work.tex
fix small things

There are many BX languages \cite{josh_pepm} \cite{BXtend} \cite{eMoflon} \cite{EVL+Strace} \cite{JTL} \cite{NMF}
%(memo: BXtend, eMoflon, EVL+Strace, JTL, NMF. SDMLib should be added?)
based on several application scenarios and BX lenses works \cite{} (add papers for lenses). The semantics and correctness of bidirectional programs has been investigated intensively during the past years, but their efficiency and optimization are not yet fully understood. Anjorin et. al. introduces the first benchmark for BX languages and compared them \cite{BXcomp}. However, the improvement for practical implementation of BX languages is still missing. As a first step, we study different evaluation methods to optimized their evaluation. We can say this paper will be first attempt to improve efficiency of BX composition evaluation. In this paper we focus on a BX language BiGUL \cite{josh_pepm} \cite{josh_popl}, we compare BiGUL's method (in Section 2) and our methods (in Section 3 and 4). From experimental results of left associative programs, we know that our memoization methods are faster than the original BiGUL's evaluation method.
In this paper we focus on BiGUL, however our methods can be applicable to other BX languages which have similar problems.

@@

Memoization \cite{} is well-known technique to reduce extra evaluation. In our case, simple application of memoization $put_m$ works well for many BX programs.
Another way to reduce extra evaluation is fusion \cite{}. However, fusion of BX programs are not considered well \textcolor{red}{(really?)}. Therefore we do not use this way.
  Instead of that, we introduce another way: using tupling \cite{}, lazy update and lazy computation \cite{}. Tupling \cite{tupling} is often used for reducint common evaluations, but we use it for reducing the size of complements.
  Lazy evaluation \cite{} is also a well-known and widly-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.

>>>>

There are many BX languages \cite{josh_pepm} \cite{BXtend} \cite{eMoflon} \cite{EVL+Strace} \cite{JTL} \cite{NMF}
%(memo: BXtend, eMoflon, EVL+Strace, JTL, NMF. SDMLib should be added?)
based on several application scenarios and BX lenses works \cite{} \textcolor{red}{(add papers for lenses)}. The semantics and correctness of bidirectional programs has been investigated intensively during the past years, but their efficiency and optimization are not yet fully understood. Anjorin et. al. introduces the first benchmark for BX languages and compared them \cite{BXcomp}. However, the improvement for practical implementation of BX languages is still missing. As a first step, we study different evaluation methods to optimized their evaluation. We can say this paper will be first attempt to improve efficiency of BX composition evaluation. In this paper we focus on a BX language BiGUL \cite{josh_pepm} \cite{josh_popl}, we compare BiGUL's method (in Sect. 2) and our methods (in Sect. 3 and 4). From experimental results of left associative BX composition programs, we know that our memoization methods are faster than the original BiGUL's evaluation method.
In this paper we focus on BiGUL, however our methods can be applicable to other BX languages which have similar problems.

@@

Memoization \cite{} is well-known technique to reduce extra evaluation. In our case, simple application of memoization $put_m$ works well for many BX programs.
Another way to reduce extra evaluation is fusion \cite{}. However, fusion of BX programs are not considered well \textcolor{red}{(really?)}. Therefore we do not use this way.
  Instead of that, we introduce another way: using tupling \cite{}, lazy update and lazy computation \cite{}. Tupling \cite{tupling} is often used for reducing common evaluations, but we use it for reducing the size of complements.
  Lazy evaluation \cite{} is also a well-known and widely-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.

### 2019-11-27 paper/7.conclusion.tex
fix small things

In this paper, we focus on efficiency of composition of BX programs.
To achieve fast evaluation, we introduce two different methods using memoization.
From the experimental results of left associative composition of BX programs, we know that $put_m$ is fastest method if input size is not very big and $xpg$ is fastest for other left associative programs.
This shows that if programmer choose one method based on the their BX programs and inputs, they can use efficient evaluation.

@@

We will continue our work on the following points.
First is overcomming our limitation in $xpg$. In $xpg$, there are several limitations: only very-well-behaved programs, path problem (shown in Section ..). To be a practical evlauation method, extention is needed. After extention of the language, we can evaluate more interesting programs for experimental results.

Second is analysis about BX programs and inputs to choose the best evaluation method automatically.
Currently, programmers have to choose the evaluation method by themselves based on their BX programs and inputs. If automatic choice is possible, we can reduce programmer's burden.

\begin{itemize}
\item construct\_dummy?
\end{itemize}

>>>>

In this paper, we focus on efficiency of composition of BX programs.
To achieve fast evaluation, we introduce two different methods using memoization.
From the experimental results of left associative BX composition programs, we know that $put_m$ is fastest method if input size is not very big and $xpg$ is fastest for other left associative programs.
This shows that if programmer choose one method based on the their BX programs and inputs, they can use efficient evaluation.

@@

We will continue our work on the following two points.
First is overcomming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs, restriction for $\pginline{Case}$ (shown in Sect. 4.1). To be a practical evlauation method, extention of the target language is needed. After extention of the language, we can evaluate more interesting programs for experimental results.

Second is introducing analysis about BX programs and inputs to choose the best evaluation method automatically.
Currently, programmers have to choose the evaluation method by themselves based on their BX programs and inputs. If automatic choice is possible, we can reduce programmer's burden.

\begin{itemize}
\item $construct\_dummy$??
\end{itemize}
